Open-source landscape for 3D CSEM modelling

### 2020-10-12 manuscript/Manuscript.tex

\documentclass[
    paper,
%     manuscript,
     twocolumn,
     twoside,
%     revised,
  ]{geophysics}

@@

The actual differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_medium} for almost the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest. The dimension of the computational domain varies for the different meshes:
% emg3d:         x = 327 to 454 km; z =  -57 to 83 km
% SimPEG:        x = 288 to 492 km; z = -123 to 41 km
% custEM/PETGEM: as shown in the image (+/- 25 km)
\plot*{results-marlim_medium}{width=\textwidth}{Meshes (left column), broadside $E_x$ field (middle column), and broadside $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row). The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger. (Vertical exaggeration: 1.1.)}
%
The top rows show the rectilinear mesh of \emg3d, the middle rows the octree mesh of \simpeg, and the bottom rows the tetrahedra mesh of \custem and \petgem. The actual mesh, the $|E_x|$ field, and the $|E_y|$ field are shown in the left, middle, and right columns, respectively.

%
\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain. (Vertical exaggeration: 4.1.)}

@@

\paragraph{TODOs:}
Figure \ref{fig:results-marlim_allmodels} is just added; integrate properly. Also, the following info should be integrated:
\begin{itemize}
    \item Model interpolation: \simpeg and \emg3d use volume averaging on log10(rho)-space; \custem and \petgem use linear interpolation on log10(rho)-space.
    \item Fields interpolation: \simpeg uses ???\mycom[DW]{Lindsey, what did you use in the end?}; \emg3d uses spline interpolation; the FE codes custEM and PETGEM use the second-order basis functions for the interpolation within elements. 
\end{itemize}
\plot*{results-marlim_allmodels}{width=\textwidth}{TODO (Vertical exaggeration: 3.6.)}

@@

We would like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.

>>>>

\documentclass[
    paper,
%     manuscript,
%     twocolumn,
%     twoside,
%     revised,
  ]{geophysics}

@@

The actual differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_big} for almost the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest. The dimension of the computational domain varies for the different meshes:
% emg3d:         x = 327 to 454 km; z =  -57 to 83 km
% SimPEG:        x = 288 to 492 km; z = -123 to 41 km
% custEM/PETGEM: as shown in the image (+/- 25 km)
\plot*{results-marlim_big}{width=\textwidth}{Meshes (left column), broadside $E_x$ field (middle column), and broadside $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row). The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
%
The top rows show the rectilinear mesh of \emg3d, the middle rows the octree mesh of \simpeg, and the bottom rows the tetrahedra mesh of \custem and \petgem. The actual mesh, the $|E_x|$ field, and the $|E_y|$ field are shown in the left, middle, and right columns, respectively.

%
\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain (3$\times$ vertical exaggeration).}

@@

\paragraph{TODOs:}
Figure \ref{fig:results-marlim_allmodels} is just added; integrate properly. Also, the following info should be integrated:
\begin{itemize}
    \item Model interpolation: \simpeg and \emg3d use volume averaging on log10(rho)-space; \custem and \petgem use linear interpolation on log10(rho)-space.
    \item Fields interpolation: \simpeg uses ???\mycom[DW]{Lindsey, what did you use in the end?}; \emg3d uses spline interpolation; the FE codes custEM and PETGEM use the second-order basis functions for the interpolation within elements. 
\end{itemize}
\plot*{results-marlim_allmodels}{width=\textwidth}{TODO (3$\times$ vertical exaggeration).}

@@

We had help of several colleagues for different tasks, and would therefore like to thank Bane Sullivan (plotting of tetrahedra in matplotlib through PyVista), Seogi Kang (octree meshes), \mycom[DW]{please add if someone helped with something}. We would also like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.
